Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/introduction.tex
Fixed a small issue in Protocol 1

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
\For{$t=1,2,\dots,T$}{
     Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
     Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.
     Observe feedback
          $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
%$z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
%0 & \text{if $\widehat y_t = y_t$,} \\
%1 & \text{if $\widehat y_t \neq y_t$.}
%\end{cases}$
}

>>>>

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
\For{$t=1,2,\dots,T$}{
     Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
     Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
     Observe feedback
          $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
%$z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
%0 & \text{if $\widehat y_t = y_t$,} \\
%1 & \text{if $\widehat y_t \neq y_t$.}
%\end{cases}$
}
